### 2020-07-20 code/figure1.Rmd
typo in Figure 1C data umap output

rngtools::setRNG(r)
gdc.umap <- uwot::umap(mca_res$ind$coord, 
                       n_components = 3,
                       n_neighbors = round(sqrt(nrow(mca_res$ind$coord))), # 87
                       n_epochs = 1000,
                       n_threads = 1)
gdc_umap_coors <- as.data.frame(plotting_umap) %>%
  rename(plot_x = V1, plot_y = V2, plot_z = V3)

>>>>

rngtools::setRNG(r)
gdc.umap <- uwot::umap(mca_res$ind$coord, 
                       n_components = 3,
                       n_neighbors = round(sqrt(nrow(mca_res$ind$coord))), # 87
                       n_epochs = 1000,
                       n_threads = 1)
gdc_umap_coors <- as.data.frame(gdc.umap) %>%
  rename(plot_x = V1, plot_y = V2, plot_z = V3)
